---
title: "Which is the best state in the database to sell a popular brand car and why?"
author: "Rafael"
date: "2023-07-15"
output: html_document
---
# Loading packages and dataset
```{r package, message=FALSE, results='hide'}
pacotes <- c("readxl", "dplyr", "ggplot2" )
lapply(pacotes, library, character.only = TRUE)
```
```{r load}
cars_train <- read_excel("cars_train.xlsx")
```

# Analyses
Using `table` to look at the available brands:
```{r table}
table(cars_train$marca)
```

I'll consider the term "popular" as a reference to brands that have more affordable cars in Brazil.

## Creating a new dataset with only "popular" brands 
```{r populares}
populares <- filter(cars_train, marca %in% c("CHEVROLET", "FIAT", "FORD", "HONDA", "HYUNDAI", "JEEP", "KIA", "NISSAN", "PEUGEOT", "RENAULT", "TOYOTA", "VOLKSWAGEN"))
```

## Aggregating observations by "estado_vendedor" and showing a ranking of states with the highest number of observations
```{r rank}
vendas_por_estado <- populares %>%
  group_by(estado_vendedor) %>%
  summarise(total_vendas = n()) %>%
  arrange(desc(total_vendas))
  top_10_estados <- head(vendas_por_estado, 10)
  top_10_estados
```

## Getting the highest price for each "estado_vendedor"
```{r vendas2}
maior_preco_por_estado <- populares %>%
  group_by(estado_vendedor) %>%
  summarize(maior_preco = max(preco)) %>%
arrange(desc(maior_preco))
maior_preco_por_estado
```

## Calculating the standard deviation for each "estado_vendedor"
```{r vendas3}
desvio_padrao_por_estado <- populares %>%
  group_by(estado_vendedor) %>%
  summarize(desvio_padrao = sd(preco)) %>%
arrange(desc(desvio_padrao))
desvio_padrao_por_estado
```

## Calculating the average price for each state
```{r media}
populares_top_estados <- filter(populares, estado_vendedor %in% top_10_estados$estado_vendedor)
media_preco_por_estado <- populares_top_estados %>%
  group_by(estado_vendedor) %>%
  summarize(media_preco = mean(preco))
  media_preco_por_estado
```

## Creating a boxplot of prices for the top 5 states with the most sales
```{r box}
siglas_estados <- c("AL", "BA", "GO", "MG", "PR", "PE", "RJ", "RS", "SC", "SP" )
ggplot(populares_top_estados, aes(x = estado_vendedor, y = preco)) +
  geom_boxplot() +
  labs(title = "Boxplot dos Preços dos Carros Populares",
       x = "Estado Vendedor",
       y = "Preço") +
  scale_x_discrete(labels = siglas_estados) +
  scale_y_continuous(labels = scales::comma)
```

We can observe that the state of São Paulo had a significantly higher number of observations compared to other states. Furthermore, although the average selling price is similar among the top ten states with the most observations, São Paulo has the highest selling price for a popular brand car. The standard deviation also indicates reasonable price variability, suggesting that sellers can get good deals when selling their cars in the state of São Paulo.

Given that the difference in average prices for popular cars between states is relatively small, it is more advantageous to sell the car in the state with the highest number of observations. In this case, the seller would have an easier time closing the sale and would likely receive more offers to choose from, which may be more attractive.

Therefore, based on the analysis of the dataset, we can conclude that São Paulo is the most favorable state to sell a popular brand car, mainly due to the significant difference in the number of observations compared to other states.

It's worth noting that this analysis considered only the "popular" brands in the "cars_train" dataset, which are: "CHEVROLET," "FIAT," "FORD," "HONDA," "HYUNDAI," "JEEP," "KIA," "NISSAN," "PEUGEOT," "RENAULT," "TOYOTA," and "VOLKSWAGEN."