---
title: "What is the best state to buy an automatic transmission pickup truck and why?"
author: "Rafael"
date: "2023-07-15"
output: html_document
---
# Loading packages and dataset
```{r package, message=FALSE, results='hide'}
pacotes <- c("readxl", "dplyr")
lapply(pacotes, library, character.only = TRUE)
```
```{r load}
cars_train <- read_excel("cars_train.xlsx")
```

# Analyses
Using `table` to look at the available types
```{r table}
table(cars_train$tipo)
```
.
## Creating a new dataset with only the "picape"(pickup truck) type
```{r picapes}
picapes_auto <- filter(cars_train, tipo %in% c("Picape"))
```

## Filtering the "picapes_auto" dataset to contain only automatic pickups 
```{r picapes2}
picapes_auto <- filter(picapes_auto, cambio %in% c("Automática"))
```

## Looking at the observations for each "estado_vendedor"(selling state)
```{r vendas}
vendas_por_estado <- picapes_auto %>%
  group_by(estado_vendedor) %>%
  summarize(volume_vendas = n()) %>%
  arrange(desc(volume_vendas))
vendas_por_estado
```

## Obtaining the lowest price for each "estado_vendedor"
```{r vendas2}
menor_preco_por_estado <- picapes_auto %>%
  group_by(estado_vendedor) %>%
  summarize(menor_preco = min(preco)) %>%
arrange(menor_preco)
menor_preco_por_estado
```

## Calculating the standard deviation for each "estado_vendedor"
```{r vendas3}
desvio_padrao_por_estado <- picapes_auto %>%
  group_by(estado_vendedor) %>%
  summarize(desvio_padrao = sd(preco)) %>%
arrange(desc(desvio_padrao))
desvio_padrao_por_estado
```

## Calculating the average selling price for each "estado_vendedor"
```{r preço}
preco_medio_por_estado <- picapes_auto %>%
  group_by(estado_vendedor) %>%
  summarize(preco_medio = mean(preco)) %>%
  arrange(preco_medio)
preco_medio_por_estado
```

It is observed that the state of Paraíba has the lowest average price for automatic pickup trucks. However, it is important to note that the state of Paraíba has only four automatic pickup trucks in the dataset, which makes the sample size small and may indicate difficulty in finding automatic pickup trucks for purchase.

On the other hand, the state of São Paulo has the highest number of observations for automatic pickup trucks. Furthermore, it also has the lowest absolute value among all automatic pickup trucks available, one of the highest standard deviations in the prices of these vehicles, and only the eighth-highest average price out of 18 states.

Therefore, overall, the state of São Paulo is the best state to buy an automatic pickup truck. It is where a person would have the easiest time finding an automatic pickup truck to purchase, and due to the significant variability in prices indicated by the standard deviation, the person would also have the opportunity to find relatively lower prices than in other states.

It is important to note that this analysis was conducted only with observations that had the category "Picape"(pickup truck) in the qualitative variable "tipo"(type) and "Automática"(automatic) in the qualitative variable "cambio"(trasmission).