---
title: "Considering a luxury dealership that sells only one brand, which would be the brand and the state, excluding São Paulo, most suitable to open this luxury dealership?"
author: "Rafael"
date: "2023-07-15"
output: html_document
---
# Loading packages and dataset
```{r package, message=FALSE, results='hide'}
pacotes <- c("readxl", "dplyr")
lapply(pacotes, library, character.only = TRUE)
```
```{r load}
cars_train <- read_excel("cars_train.xlsx")
```

# Analyses
Usando `table` para olhar as marcas disponíveis:
```{r table}
table(cars_train$marca)
```

## Creating a new dataset only with luxury brands: 
```{r populares}
luxo <- filter(cars_train, marca %in% c("ALFA ROMEO", "AUDI", "BMW", "CHRYSLER", "FERRARI", "JAGUAR", "LAND ROVER", "LEXUS", "MASERATI", "MERCEDES-BENZ", "PORSCHE"))
```

## States with the highest volumes of observations for luxury cars
```{r rank}
vendas_por_estado <- luxo %>%
  group_by(estado_vendedor) %>%
  summarise(total_vendas = n()) %>%
  arrange(desc(total_vendas))
  top_10_estados <- head(vendas_por_estado, 10)
  top_10_estados
```

## Calculating the average price of “luxury” cars for each state
```{r media}
luxo_top_estados <- filter(luxo, estado_vendedor %in% top_10_estados$estado_vendedor)
media_preco_por_estado <- luxo_top_estados %>%
  group_by(estado_vendedor) %>%
  summarize(media_preco = mean(preco)) %>%
  arrange(desc(media_preco))
  media_preco_por_estado
```

## Counting the number of observations by brand and state in the “luxo” dataset
```{r rank2}
vendas_por_marca_estado <- luxo %>%
  group_by(estado_vendedor, marca) %>%
  count() %>%
  arrange(estado_vendedor, desc(n))
marca_mais_vendida_por_estado <- vendas_por_marca_estado %>%
  group_by(estado_vendedor) %>%
  slice(1) %>%
  ungroup() %>%
  arrange(desc(n))
marca_mais_vendida_por_estado
```

Analyzing the “cars_train” dataset, we observe that the state of Paraná has the second highest volume of observations and the second highest average price for luxury cars. Knowing that the state of São Paulo is not being considered, we can conclude that, based on this data, the state of Paraná would be a favorable choice to open the dealership.

The BMW brand stands out as the most sold in the state of Paraná, demonstrating that a luxury dealership opened in this state should focus on selling BMW brand cars.

It is important to note that we did not specifically evaluate the average price of BMW brand cars, but rather the average price of luxury cars in general. Thus, as Paraná has the highest average price for luxury cars, we can infer that the population of this state has a good acceptance to pay higher values for luxury cars. In addition, the preference of Paraná residents for the BMW brand provides another indication for choosing this brand at the dealership.

These combined indicators provide a solid basis for making the decision to open a luxury dealership in the state of Paraná focused on the BMW brand.