---
title: "Statistical Analysis"
author: "Rafael"
date: "2023-07-16"
output: html_document
---
# Loading packages and datasets, and removing columns related to "id"
```{r package, message=FALSE, results='hide'}
pacotes <- c("readxl", "PerformanceAnalytics")
lapply(pacotes, library, character.only = TRUE)
```

```{r load}
cars_train <- read_excel("cars_train.xlsx")
cars_test <- read_excel("cars_test.xlsx")
```

```{r remove}
cars_train <- cars_train[-1]
cars_test <- cars_test[-1]
```

# Calculating and displaying the correlation matrix
```{r correlation, warning=FALSE}
chart.Correlation((cars_train[, c(1, 5:7, 9, 28)]), histogram = TRUE)
```

The correlation matrix allows us to understand the relationship that numeric variables maintain with each other. We can see that "num_fotos" and "num_portas" have low correlation with all the others and have little influence on the price of the cars.

Interestingly, "num_portas" shows a slight negative correlation with price, which may seem counterintuitive due to the common perception that cars with more doors tend to be more expensive because they are larger, etc. However, the data exhibit this behavior due to the presence of observations representing luxury sports cars with two doors that have a very high value.

The other numeric variables follow an expected pattern. "ano_de_fabricacao" has a strong positive correlation with "ano_modelo", and both have a positive correlation with price, indicating that the newer the car, the higher its price tends to be.

The "hodometro" variable also follows an expected pattern, showing a negative correlation with "ano_de_fabricacao", "ano_modelo", and "preco". We can infer that older cars tend to have a higher odometer(hodometro in portuguese) reading. Consequently, the higher the odometer reading, the lower the price of the automobile.

This brief analysis shows us that the numeric variables, in general, have reliable and coherent relationships with reality.

# Analysis of Variance 

```{r anova}
anova <- aov(preco ~ marca, data = cars_train) 
summary(anova)                                      
```

<span style="font-size: smaller;"> _If we wish to analyze a different variable than "marca", simply replace "marca" with the desired variable's name._

Analysis of variance (ANOVA) is useful for assessing the significance of one variable in relation to another, allowing for a clear understanding of the relationships between variables. When used in conjunction with correlation analyses, we obtain a comprehensive overview of the relationships between variables.

Using the "aov" function, it was possible to analyze all independent variables in relation to the dependent variable "price".

The results indicated that virtually all variables were significant for price formation at a 95% confidence level. The only variables that were not significant at a 95% confidence level were "elegivel_revisao", "ipva_pago", and "veiculo_alienado".

# Displaying statistics of the variables
```{r summary}
summary(cars_train)
summary(cars_test)
```

Through the `summary` function, we can view statistical information about the variables in the 'cars_train' and 'cars_test' datasets. It provides the type of each variable, as well as the range and statistical information such as mean, median, and quartiles for the numeric variables.

After analyzing the dataset using the 'summary' function, we can observe some relevant information. For example, the mean price of cars is $133,024. Additionally, we notice that the dataset contains observations representing very recent cars with a model year of 2023, as well as observations related to older cars with a manufacturing year as early as 1985.

We also observe considerable variation in the odometer readings of the cars in the dataset. Some cars have very low mileage, suggesting limited use, while others have quite high mileage, indicating more extensive use.

Thus, using `summary` allows us to get an overview of the characteristics and distribution of the variables. These statistical insights are helpful for better understanding the data and identifying potential discrepancies, outliers, or patterns in the variable values.

# Displaying the categories/levels of qualitative variables
```{r levels}
levels(factor(cars_train$marca)) 
levels(factor(cars_test$marca))  
```

<span style="font-size: smaller;"> _If we wish to analyze a variable other than 'marca', simply replace 'marca' with the desired variable's name._

The "levels" function allows us to identify the number of categories/levels present in qualitative/categorical variables. This function is useful because, when combined with other analyses, it provides us with a good understanding of the complexity of the data we are dealing with.

In this particular case, we observe that some of the qualitative variables have a large number of categories, with particular emphasis on the "versao" (version) variable.

This indicates that training a predictive model will be challenging, as these variables increase the complexity of the model and should be included in the training process. We know, both from the analyses conducted here and our real-world experience, that variables such as model, version, and car brand have a direct influence on the price.

It's also worth noting that the categories of the qualitative variables are not exactly the same in both datasets. For example, the "BRM" category in the "marca" (brand) variable is exclusive to the "cars_train" dataset. Therefore, special data treatment will be necessary to make price predictions in the "cars_test" dataset using a model trained on the "cars_train" dataset.

# Displaying the frequencies of each category/level of the qualitative variables
```{r table}
table(cars_train$marca)         
table(cars_test$marca)          
```

<span style="font-size: smaller;"> _If we want to analyze a different variable than "marca" (brand), simply replace "marca" with the name of the desired variable._

The `table` function is also very useful for obtaining information about qualitative variables. It allows us to check the count of observations in each of the categories of a qualitative variable.

When analyzing the data, we noticed that variables with a larger number of categories have some categories with a very small number of observations. Specifically, the "versao" (version) variable has several categories with few observations.

As mentioned earlier, this characteristic in a dataset can make predictions more challenging, especially when we cannot simply exclude the variables that exhibit these characteristics.
