---
title: "What is the best state to buy cars that are still under factory warranty and why?"
author: "Rafael"
date: "2023-07-15"
output: html_document
---
# Loading packages and dataset
```{r package, message=FALSE, results='hide'}
pacotes <- c("readxl", "dplyr")
lapply(pacotes, library, character.only = TRUE)
```
```{r load}
cars_train <- read_excel("cars_train.xlsx")
```

# Analyses
Using table to look at the frequencies of the variable “garantia_de_fábrica”( factory warranty)
```{r table}
table(cars_train$garantia_de_fábrica)
```
.
## Creating a new dataset only with cars that still have factory warranty
```{r garantia}
garantia <- filter(cars_train, garantia_de_fábrica %in% c("Garantia de fábrica"))
```

## Looking at the volume of observations for each “estado_vendedor”(selling state)
```{r vendas}
vendas_por_estado <- garantia %>%
  group_by(estado_vendedor) %>%
  summarize(volume_vendas = n()) %>%
  arrange(desc(volume_vendas))
print(vendas_por_estado, n = Inf)
```

## Getting the lowest price for each “estado_vendedor”
```{r vendas2}
menor_preco_por_estado <- garantia %>%
  group_by(estado_vendedor) %>%
  summarize(menor_preco = min(preco)) %>%
arrange(menor_preco)
print(menor_preco_por_estado, n = Inf)
```

## Calculating the standard deviation for each “estado_vendedor”
```{r vendas3}
desvio_padrao_por_estado <- garantia %>%
  group_by(estado_vendedor) %>%
  summarize(desvio_padrao = sd(preco)) %>%
arrange(desc(desvio_padrao))
print(desvio_padrao_por_estado, n = Inf)
```

## Calculating the average selling price for each “estado_vendedor”
```{r preço}
preco_medio_por_estado <- garantia %>%
  group_by(estado_vendedor) %>%
  summarize(preco_medio = mean(preco)) %>%
  arrange(preco_medio)
print(preco_medio_por_estado, n = Inf)
```

Once again, the state of São Paulo demonstrates, in general, the most interesting metrics for the goal at hand. Besides having the largest volume of observations, São Paulo also presents one of the cars with a warranty at one of the lowest prices.

In the ranking of the average prices of cars with a warranty by state, São Paulo occupies the thirteenth position. However, if we consider only the five states with the highest number of cars with a warranty, São Paulo would be in first place. As for the standard deviation, it indicates that São Paulo has a moderate variability in prices compared to other states.

These metrics indicate that, based on the analyzed data, São Paulo is the most suitable state for purchasing factory warranty cars. It's where you would find the largest number of available options, as well as having a reasonable average price. Additionally, the high number of observations and a reasonably wide standard deviation suggest that the buyer would have good chances of finding opportunities at lower prices, provided they were willing to search for them.

It's important to note that this analysis was conducted only with observations that had the category "Garantia de Fábrica" in the qualitative variable "garantia_de_fábrica."