---
title: "Excluding São Paulo, which is the best state to buy cars from individuals that have paid IPVA?"
author: "Rafael"
date: "2023-07-15"
output: html_document
---
# Loading packages and dataset
```{r package, message=FALSE, results='hide'}
pacotes <- c("readxl", "dplyr", "ggplot2")
lapply(pacotes, library, character.only = TRUE)
```
```{r load}
cars_train <- read_excel("cars_train.xlsx")
```

# Analyses

# Looking at the states with the highest numbers of cars with paid IPVA whose sellers are individuals
```{r table}
ipvas <- cars_train %>%
  group_by(estado_vendedor) %>%
  filter(ipva_pago == "IPVA pago" & tipo_vendedor == "PF") %>%
  summarize(total_carros = n()) %>%
  arrange(desc(total_carros))
ipvas
```

# Filtering only the five states with the highest numbers of cars with paid IPVA
```{r table2}
top_5_estados <- head(ipvas, 5)$estado_vendedor
dados_top_5 <- filter(cars_train, estado_vendedor %in% top_5_estados & ipva_pago == "IPVA pago")
```

# Creating a boxplot of the prices of the five states with the highest numbers of cars with paid IPVA whose sellers are individuals
```{r table3}
ggplot(dados_top_5, aes(x = estado_vendedor, y = preco)) +
  geom_boxplot() +
  labs(title = "Box Plot of prices per state",
       x = "State",
       y = "Price")
```

## Calculating the average price of cars with paid IPVA whose sellers are individuals in the five states with the most observations
```{r media}
media_precos_estado <- dados_top_5 %>%
  group_by(estado_vendedor) %>%
  summarize(media_preco = mean(preco)) %>%
  arrange(media_preco)
media_precos_estado
```

Considering the analyses made above, we conclude that, excluding the state of São Paulo, the state of Rio de Janeiro would be the best state to buy a car with paid IPVA whose seller is an individual.

It is noted that the state of Rio de Janeiro is the second state with the highest number of cars with such characteristics. It is also noticed that the state of Rio de Janeiro has the smallest range in its outliers.

Finally, we can see that the state of Rio de Janeiro has the second lowest average price for cars with paid IPVA whose seller is an individual.

Therefore, we can affirm that in general, and disregarding the state of São Paulo, Rio de Janeiro is the best state to buy cars with paid IPVA whose seller is an individual.